### 2020-06-05 5_evaluation.tex
Update text for "limit 50%".

We can use METG to predict the scalability of a code. Figure
\ref{fig:strong-scaling} shows strong scaling for three Task Bench
implementations with the stencil pattern. Lines marked ``actual''
represent strong scaling measurements, while ones marked ``limit'' are
computed by multiplying METG(50\%) by tasks per core (in this case,
1000). Intuitively, ``limit'' is the smallest time to solution that
can be achieved for \emph{any} problem size at that node count, while
maintaining 50\% efficiency. Note that ``actual'' eventually falls
below ``limit'' because ``actual'' is not constrained to 50\%
efficiency and eventually drops below this level.

There are two points of interest on each ``limit'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively. Notably, the intersection between ideal and ``limit''
requires only a single node run, along with measurements of METG(50\%)
at each node count. Using this data it is possible to predict the
strong scalability of the code: i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $2.15\times$ in node count
and at most $1.31\times$ in time to solution, making this an
accurate way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.

>>>>

We can use METG to predict the scalability of a code. Figure
\ref{fig:strong-scaling} shows strong scaling for three Task Bench
implementations with the stencil pattern. Lines marked ``actual''
represent strong scaling measurements, while ones marked ``limit 50\%'' are
computed by multiplying METG(50\%) by tasks per core (in this case,
1000). Intuitively, ``limit'' is the smallest time to solution that
can be achieved for \emph{any} problem size at that node count, while
maintaining 50\% efficiency. Note that ``actual'' eventually falls
below ``limit'' because ``actual'' is not constrained to 50\%
efficiency and eventually drops below this level.

There are two points of interest on each ``limit 50\%'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively. Notably, the intersection between ideal and ``limit 50\%''
requires only a single node run, along with measurements of METG(50\%)
at each node count. Using this data it is possible to predict the
strong scalability of the code: i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $2.15\times$ in node count
and at most $1.42\times$ in time to solution, making this an
accurate way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.
